\chapter{Design and Implementation}

\todo[inline]{Contains only brief notes.}

\todo[inline]{Outline considerations when migrating desktop education tool to accessible, usable, extendable, secure, and reproducible web application.}

\todo[inline]{Consider mentioned hurdles with MOOC development.}

\section{Accessibility and Usability}

\todo[inline]{Designed to be usable with built-in accessibility tools shown to be used by primary and secondary beneficiaries.}

\todo[inline]{Main points: semantics, ARIA. Figures are SVGs with system-stack fonts and not curves.}

\todo[inline]{Include https://www.w3.org/WAI/about/accessibility-statement/ and https://www.w3.org/WAI/meta/customize/.}

Performance/size related:

\todo[inline]{Bandwith/internet connection (Accessibility benefits backreference)}.

\todo[inline]{Time to first interaction.}

\todo[inline]{Minimal build size - Svelte via SvelteKit and Tailwind with three shaking, chunking, server side rendering (static build).}

\todo[inline]{Used bandwith and required internet connection.}

\todo[inline]{Compare size and time to download the Nand2Tetris desktop (with and without JRE) app and the highly-optimised web app.}

\todo[inline]{Contrary to expectations - web app does not have to be downloaded again - can be used offline as PWA.}

\todo[inline]{So faster to load than both nand2tetris and wepsim and is loaded only once/works offline like nand2teris and unlike wepsim.}

Client device supported:

\todo[inline]{Usable from all platforms - percentage? Compare to Nand2Tetris.}

\todo[inline]{Progressive enhancement.}

\todo[inline]{IDE - Monaco for accessibility and powerful capabilities. Link back to Literature Review - Monaco at the hearth of the most popular VSCode.}

\section{Extensibility}

\todo[inline]{Everything (including learning materials) control versioned on Github.}
\todo[inline]{Learning materials processed from Markdown files using Markdoc.}

\section{Acceleration of Development}

\todo[inline]{Use of available third party libraries to accelerate development.}

\todo[inline]{Nearley with Moo for simple and powerful parser. Still performant - regex, linear complexity right recursion.}

\todo[inline]{Use of freely available scalable services - Github, Cloudflare - CDN, CI/CD, key/value.}

\section{Security}

\todo[inline]{Infrastructure and deployment: DNSSEC, HTTPS, automation - CI/CD with signed commits - open source considerations!, "Denial of Wallet".}

\todo[inline]{Anonymous sessions via secure-only http-only cookies.}

\todo[inline]{Parsers and interpreters: No eval or access to arbitrary JS APIs in interpreter.}

\section{Reproducibility}

\todo[inline]{Again - everything is versioned - infrastructure, documentation, content, code.}

\todo[inline]{Made for easy hosting by anybody even without the backend.}

\todo[inline]{Backend optional - can be swapped for other provider.}
